P versus NP

### 2019-11-25 doc/manuscript.tex
Updated revision proof

\begin{hypothesis}
\label{hypothesis1}
Given a language $L_{1} \in L$, there is a language $L_{2}$ in $\textit{NP--complete}$ with a deterministic Turing machine $M$, where:
\[L_{2} = \{w: M(w, u) = y \textit{ for some string } u \textit{ such that } y \in L_{1}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$. In this way, there is an $\textit{NP--complete}$ language defined by a logarithmic space verifier $M$ such that when the input is an element of the language with its certificate, then $M$ outputs a string which belongs to a single language in $L$.
\end{hypothesis}

@@

\begin{hypothesis}
\label{hypothesis2}
Given a language $L_{1} \in 1NL$, there is a language $L_{2}$ in $\textit{coNP--complete}$ with a deterministic Turing machine $M$, where:
\[L_{2} = \{w: M(w, u) = y \textit{ for all the appropriated string } u \textit{ such that } y \in L_{1}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$. In this way, there is a $\textit{coNP--complete}$ language defined by a logarithmic space disqualifier $M$ such that when the input is an element of the language with any of its appropriated disqualification, then $M$ always outputs a string which belongs to a single language in $1NL$.
\end{hypothesis}

@@

\begin{definition}
$\textbf{MINIMUM EXCLUSIVE-OR 2-SATISFIABILITY}$

@@

QUESTION: Is there a truth assignment in $\phi$ such that at most $K$ clauses are unsatisfiable?

REMARKS: We denote this problem as $MIN\oplus2SAT$.
\end{definition}

\begin{theorem}
\label{completeness}
$MIN\oplus2SAT \in \textit{NP--complete}$.
\end{theorem}

\begin{proof}
It is trivial to see $MIN\oplus2SAT \in NP$ \cite{Pap03}. Given a Boolean formula $\phi$ in $3CNF$ with $n$ variables and $m$ clauses, we create three new variables $a_{c_{i}}$, $b_{c_{i}}$ and $d_{c_{i}}$ for each clause $c_{i} = (x \vee y \vee z)$ in $\phi$, where $x$, $y$ and $z$ are literals, in the following formula:
\[P_{i} = (a_{c_{i}} \oplus b_{c_{i}}) \wedge (b_{c_{i}} \oplus d_{c_{i}}) \wedge (a_{c_{i}} \oplus d_{c_{i}}) \wedge (x \oplus a_{c_{i}}) \wedge (y \oplus b_{c_{i}}) \wedge (z \oplus d_{c_{i}}).\]
We can see $P_{i}$ has at most one unsatisfiable clause for some truth assignment if and only if at least one member of $\{x,y,z\}$ is true and at least one member of $\{x,y,z\}$ is false for the same truth assignment. Hence, we can create the Boolean formula $\psi$ as the conjunction of the $P_{i}$ formulas for every clause $c_{i}$ in $\phi$, such that $\psi = P_{1} \wedge \ldots \wedge P_{m}$. Finally, we obtain that
\[\phi \in \textit{NAE 3SAT} \textit{ if and only if } (\psi, m) \in MIN\oplus2SAT.\]
Consequently, we prove $\textit{NAE 3SAT} \leq_{p} MIN\oplus2SAT$ where we already know the language $\textit{NAE 3SAT} \in \textit{NP--complete}$ \cite{GJ79}. To sum up, we show $MIN\oplus2SAT \in \textit{NP--hard}$ and $MIN\oplus2SAT \in NP$ and thus, $MIN\oplus2SAT \in \textit{NP--complete}$.
\end{proof}

\begin{theorem}
\label{proof}
There is a deterministic Turing machine $M$, where:
\[MIN\oplus2SAT = \{w: M(w, u) = y \textit{ for some string } u \textit{ such that } y \in \textit{XOR 2SAT}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
\end{theorem}

\begin{proof}
Given a valid instance $(\psi, K)$ for $MIN\oplus2SAT$ when $\psi$ has $m$ clauses, we can create a certificate array $A$ which contains $K$ different natural numbers in ascending order which represents the indexes of the clauses in $\psi$ that we are going to remove from the instance. We read at once the elements of the array $A$ and we reject whether this is not an appropriated certificate: That is when the numbers are not sorted in ascending order, or the array $A$ does not contain exactly $K$ elements, or the array $A$ contains a number that is not between $1$ and $m$. While we read the elements of the array $A$, we remove the clauses from the instance $(\psi, K)$ for $MIN\oplus2SAT$ just creating another instance $\phi$ for $\textit{XOR 2SAT}$ where the Boolean formula $\phi$ does not contain the $K$ different indexed clauses $\psi$ represented by the numbers in $A$. Therefore, we obtain the array $A$ should be valid according to the Theorem \ref{proof} when:
\[(\psi, K) \in MIN\oplus2SAT \textit{ if and only if } \phi \in \textit{XOR 2SAT}.\]
Furthermore, we can make this verification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$ and we assume the clauses in the input $\psi$ are indexed from left to right. Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is an appropriated certificate and also remove the $K$ different clauses from the Boolean formula $\psi$ when we write the final clauses to the output. This logarithmic space verification will be the Algorithm \ref{algorithm1}. We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = undefined$. In addition, we reject immediately when the following comparisons
\[A[i] \leq max \vee A[i] < 1 \vee A[i] > m\]
hold at least into one single binary digit. Note, in the loop $j$ from $min$ to $max - 1$, we do not output any clause when $max - 1 < min$.

\begin{algorithm}
\caption{Logarithmic space verifier}\label{algorithm1}
\begin{algorithmic}[1]
\Comment{A valid instance for $MIN\oplus2SAT$ with its certificate}
\Procedure{$\textit{VERIFIER}$}{$(\psi, K), A$}
\Comment{Initialize minimum and maximum values}
\State $min \gets 1$
\State $max \gets 0$
\Comment{Iterate for the elements of the certificate array $A$}
\For{$i$}{$1$}{$K + 1$}
\If{$i = K+1$}
\Comment{There exists a $K+1$ element in the array}
\If{$A[i] \neq undefined$}
\Comment{Reject the certificate}
\State \textbf{return} $``no"$
\EndIf
\Comment{$m$ is the number of clauses in $\psi$}
\State $max \gets m + 1$
\ElsIf{$A[i] = undefined \vee A[i] \leq max \vee A[i] < 1 \vee A[i] > m$}
\Comment{Reject the certificate}
\State \textbf{return} $``no"$
\Else
\State $max \gets A[i]$
\EndIf
\Comment{Iterate for the clauses of the Boolean formula $\psi$}
\For{$j$}{$min$}{$max - 1$}
\Comment{Output the indexed $j^{th}$ clause in $\psi$}
\State \textbf{output} $``\wedge c_{j}"$
\EndFor
\State $min \gets max + 1$
\EndFor
\EndProcedure
\end{algorithmic}
\end{algorithm}
\end{proof}

@@

INSTANCE: A collection of integers $C$ such that $0 \notin C$ and every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$ (we do not take into account the symbol minus in the bit-length of the negative integers).

>>>>

\begin{hypothesis}
\label{hypothesis1}
Given a nonempty language $L_{1} \in L$, there is a language $L_{2}$ in $\textit{NP--complete}$ with a deterministic Turing machine $M$, where:
\[L_{2} = \{w: M(w, u) = y \textit{ for some string } u \textit{ such that } y \in L_{1}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$. In this way, there is an $\textit{NP--complete}$ language defined by a logarithmic space verifier $M$ such that when the input is an element of the language with its certificate, then $M$ outputs a string which belongs to a single language in $L$.
\end{hypothesis}

@@

\begin{hypothesis}
\label{hypothesis2}
Given a nonempty language $L_{1} \in 1NL$, there is a language $L_{2}$ in $\textit{coNP--complete}$ with a deterministic Turing machine $M$, where:
\[L_{2} = \{w: M(w, u) = y \textit{ for all the appropriated string } u \textit{ such that } y \in L_{1}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$. In this way, there is a $\textit{coNP--complete}$ language defined by a logarithmic space disqualifier $M$ such that when the input is an element of the language with any of its appropriated disqualification, then $M$ always outputs a string which belongs to a single language in $1NL$.
\end{hypothesis}

@@

\begin{definition}
$\textbf{MAXIMUM EXCLUSIVE-OR 2-SATISFIABILITY}$

@@

QUESTION: Is there a truth assignment in $\phi$ such that at most $K$ clauses are unsatisfied?

REMARKS: We denote this problem as $MAX\oplus2SAT$.
\end{definition}

\begin{theorem}
\label{completeness}
$MAX\oplus2SAT \in \textit{NP--complete}$.
\end{theorem}

\begin{proof}
It is trivial to see $MAX\oplus2SAT \in NP$ \cite{Pap03}. Given a Boolean formula $\phi$ in $3CNF$ with $n$ variables and $m$ clauses, we create three new variables $a_{c_{i}}$, $b_{c_{i}}$ and $d_{c_{i}}$ for each clause $c_{i} = (x \vee y \vee z)$ in $\phi$, where $x$, $y$ and $z$ are literals, in the following formula:
\[P_{i} = (a_{c_{i}} \oplus b_{c_{i}}) \wedge (b_{c_{i}} \oplus d_{c_{i}}) \wedge (a_{c_{i}} \oplus d_{c_{i}}) \wedge (x \oplus a_{c_{i}}) \wedge (y \oplus b_{c_{i}}) \wedge (z \oplus d_{c_{i}}).\]
We can see $P_{i}$ has at most one unsatisfied clause for some truth assignment if and only if at least one member of $\{x,y,z\}$ is true and at least one member of $\{x,y,z\}$ is false for the same truth assignment. Hence, we can create the Boolean formula $\psi$ as the conjunction of the $P_{i}$ formulas for every clause $c_{i}$ in $\phi$, such that $\psi = P_{1} \wedge \ldots \wedge P_{m}$. Finally, we obtain that
\[\phi \in \textit{NAE 3SAT} \textit{ if and only if } (\psi, m) \in MAX\oplus2SAT.\]
Consequently, we prove $\textit{NAE 3SAT} \leq_{p} MAX\oplus2SAT$ where we already know the language $\textit{NAE 3SAT} \in \textit{NP--complete}$ \cite{GJ79}. To sum up, we show $MAX\oplus2SAT \in \textit{NP--hard}$ and $MAX\oplus2SAT \in NP$ and thus, $MAX\oplus2SAT \in \textit{NP--complete}$.
\end{proof}

\begin{theorem}
\label{proof}
There is a deterministic Turing machine $M$, where:
\[MAX\oplus2SAT = \{w: M(w, u) = y \textit{ for some string } u \textit{ such that } y \in \textit{XOR 2SAT}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
\end{theorem}

\begin{proof}
Given a valid instance $(\psi, K)$ for $MAX\oplus2SAT$ when $\psi$ has $m$ clauses, we can create a certificate array $A$ which contains $K$ different natural numbers in ascending order which represents the indexes of the clauses in $\psi$ that we are going to remove from the instance. We read at once the elements of the array $A$ and we reject whether this is not an appropriated certificate: That is when the numbers are not sorted in ascending order, or the array $A$ does not contain exactly $K$ elements, or the array $A$ contains a number that is not between $1$ and $m$. While we read the elements of the array $A$, we remove the clauses from the instance $(\psi, K)$ for $MAX\oplus2SAT$ just creating another instance $\phi$ for $\textit{XOR 2SAT}$ where the Boolean formula $\phi$ does not contain the $K$ different indexed clauses $\psi$ represented by the numbers in $A$. Therefore, we obtain the array $A$ should be valid according to the Theorem \ref{proof} when:
\[(\psi, K) \in MAX\oplus2SAT \textit{ if and only if } \phi \in \textit{XOR 2SAT}.\]
Furthermore, we can make this verification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$ and we assume the clauses in the input $\psi$ are indexed from left to right. Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is an appropriated certificate and also remove the $K$ different clauses from the Boolean formula $\psi$ when we write the final clauses to the output. This logarithmic space verification will be the Algorithm \ref{algorithm1}. We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = undefined$. In addition, we reject immediately when the following comparisons
\[A[i] \leq max \vee A[i] < 1 \vee A[i] > m\]
hold at least into one single binary digit. Note, in the loop $j$ from $min$ to $max - 1$, we do not output any clause when $max - 1 < min$.

\begin{algorithm}
\caption{Logarithmic space verifier}\label{algorithm1}
\begin{algorithmic}[1]
\Comment{A valid instance for $MAX\oplus2SAT$ with its certificate}
\Procedure{$\textit{VERIFIER}$}{$(\psi, K), A$}
\Comment{Initialize minimum and maximum values}
\State $min \gets 1$
\State $max \gets 0$
\Comment{Iterate for the elements of the certificate array $A$}
\For{$i$}{$1$}{$K + 1$}
\If{$i = K+1$}
\Comment{There exists a $K+1$ element in the array}
\If{$A[i] \neq undefined$}
\Comment{Reject the certificate}
\State \textbf{return} $``no"$
\EndIf
\Comment{$m$ is the number of clauses in $\psi$}
\State $max \gets m + 1$
\ElsIf{$A[i] = undefined \vee A[i] \leq max \vee A[i] < 1 \vee A[i] > m$}
\Comment{Reject the certificate}
\State \textbf{return} $``no"$
\Else
\State $max \gets A[i]$
\EndIf
\Comment{Iterate for the clauses of the Boolean formula $\psi$}
\For{$j$}{$min$}{$max - 1$}
\Comment{Output the indexed $j^{th}$ clause in $\psi$}
\State \textbf{output} $``\wedge c_{j}"$
\EndFor
\State $min \gets max + 1$
\EndFor
\EndProcedure
\end{algorithmic}
\end{algorithm}
\end{proof}

@@

INSTANCE: A collection of integers $C$ such that $0 \notin C$ and every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$ (we do not take into account the symbol minus in counting the bit-length of the negative integers).
